---
title: "Old Faithful exploratory analysis"
author: "Allan Lui"
date: "11/11/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Introduction

The Old Faithful data set contains the waiting time between eruptions and the duration of the eruption for the Old Faithful geyser in Yellowstone National Park, Wyoming, USA.

First load the data:

```{r faithful}
df <- faithful
```

The data description is given in the table below.


```{r table, echo=F}
t <- matrix(c("eruptions","the duration of the eruption, minutes","waiting", "waiting time to next eruption, minutes"), nrow = 2, byrow=T) 
colnames(t) <- c("variable","description") 
t<- as_tibble(t)
t
```

A summary of the distributions of each variable are as follows:

```{r summary}
summary(df)
```

The marginal distributions of the variables shown below:

```{r marginal distributions}
hist(df$eruptions)
hist(df$waiting)

```


#Conclusions and further work

Both the duration of eruptions and waiting time show a bimodal distribution. In further work I will plot the scatter of the data (‘eruptions duration’ vs ‘waiting time’ ) to see whether I can detect any patterns.
